---
title: "The Interview Attendance Problem"
output: html_notebook
---

Read the data

```{r}
library(readr)
df_interview <- read_csv("Interview.csv")
head(df_interview)
```

```{r}
dim(df_interview)
```

It can be seen that there are NA values in many columns and last 5 columns are empty. So let's get rid of them first.
```{r}
df_interview <- subset(df_interview, select = -c(X24, X25, X26, X27, X28))
head(df_interview)
```

There are long names of columns, that can be quite difficult to handle. Let's change the column names.

```{r}
colnames(df_interview)
```

```{r}
new_col <- c("Date", "Client_name", "Industry", "Location",
             "Position", "SkillSet", "Interview_type", "Candidate_name",
             "Gender", "Current_location", "Job_location", "Venue_of_interview",
             "Candidate_native_location", "Permissions_obtained", "Unscheduled_meetings",
             "follow_up_attendance", "Alt_number", "Printout_taken", "Clear_details",
             "Call_letter", "Expected_attendance", "Observed_attendance", "Marital_status")
colnames(df_interview) <- new_col
colnames(df_interview)
```

```{r}
summary(df_interview)
```
All the columns, except the Date column are characters. So let us convert all into lowercase for simplicity.

```{r}
df_interview$Client_name <- sapply(df_interview$Client_name, tolower)
df_interview$Industry <- sapply(df_interview$Industry, tolower)
df_interview$Location <- sapply(df_interview$Location, tolower)
df_interview$Position <- sapply(df_interview$Position, tolower)
df_interview$SkillSet <- sapply(df_interview$SkillSet, tolower)
df_interview$Interview_type <- sapply(df_interview$Interview_type, tolower)
df_interview$Candidate_name <- sapply(df_interview$Candidate_name, tolower)
df_interview$Gender <- sapply(df_interview$Gender, tolower)
df_interview$Current_location <- sapply(df_interview$Current_location, tolower)
df_interview$Job_location <- sapply(df_interview$Job_location, tolower)
df_interview$Venue_of_interview <- sapply(df_interview$Venue_of_interview, tolower)
df_interview$Candidate_native_location <- sapply(df_interview$Candidate_native_location, tolower)
df_interview$Permissions_obtained <- sapply(df_interview$Permissions_obtained, tolower)
df_interview$Unscheduled_meetings <- sapply(df_interview$Unscheduled_meetings, tolower)
df_interview$follow_up_attendance <- sapply(df_interview$follow_up_attendance, tolower)
df_interview$Alt_number <- sapply(df_interview$Alt_number, tolower)
df_interview$Printout_taken <- sapply(df_interview$Printout_taken, tolower)
df_interview$Clear_details <- sapply(df_interview$Clear_details, tolower)
df_interview$Call_letter <- sapply(df_interview$Call_letter, tolower)
df_interview$Expected_attendance <- sapply(df_interview$Expected_attendance, tolower)
df_interview$Observed_attendance <- sapply(df_interview$Observed_attendance, tolower)
df_interview$Marital_status <- sapply(df_interview$Marital_status, tolower)

```

# Data Cleaning

Let's check each column for inconsistencies in the data

Let's check Date...
```{r}
unique(df_interview$Date)
```

There are different formats of the date here.

```{r}
library(lubridate)
df_interview$Date <- gsub("&.*", "", df_interview$Date)
df_interview$Date <- dmy(df_interview$Date)
unique(df_interview$Date)
```

Let's check Client_name...
```{r}
unique(df_interview$Client_name)
```

```{r}
df_interview$Client_name <- gsub("standard chartered bank chennai", "standard chartered bank", df_interview$Client_name)
df_interview$Client_name <- gsub("aon hewitt gurgaon", "hewitt", df_interview$Client_name)
df_interview$Client_name <- gsub("aon hewitt",  "hewitt", df_interview$Client_name)
unique(df_interview$Client_name)
```


Let's check Industry...
```{r}
unique(df_interview$Industry)
```

```{r}
df_interview$Industry <- gsub("it products and services", "it", df_interview$Industry)
df_interview$Industry <- gsub("it services", "it", df_interview$Industry)
unique(df_interview$Industry)
```

Let's check Location...
```{r}
unique(df_interview$Location)
```

```{r}
df_interview$Location <- gsub("gurgaonr", "gurgaon", df_interview$Location)
df_interview$Location <- gsub("- cochin-", "cochin", df_interview$Location)
```

```{r}
unique(df_interview$Location)
```

Let's check Position...

```{r}
unique(df_interview$Position)
```
This is okay!

Let's check Skillset
```{r}
unique(df_interview$SkillSet)
```
Too many unique values, have to deal with it later!


Let's check Interview_type
```{r}
unique(df_interview$Interview_type)
```

```{r}
df_interview$Interview_type <- gsub("scheduled walk in", "scheduled walkin", df_interview$Interview_type)
df_interview$Interview_type <- gsub("sceduled walkin", "scheduled walkin", df_interview$Interview_type)
unique(df_interview$Interview_type)
```

Let's check Current Location
```{r}
unique(df_interview$Current_location)
```

```{r}
df_interview$Current_location <- gsub("- cochin-", "cochin", df_interview$Current_location)
```

Let's check job location
```{r}
unique(df_interview$Job_location)
```
```{r}
df_interview$Job_location <- gsub("- cochin-", "cochin", df_interview$Job_location)
```

Let's check venue of interview
```{r}
unique(df_interview$Venue_of_interview)
```
```{r}
df_interview$Venue_of_interview <- gsub("- cochin-", "cochin", df_interview$Venue_of_interview)
```

Let's check Candidate native location
```{r}
unique(df_interview$Candidate_native_location)
```

```{r}
df_interview$Candidate_native_location <- gsub("delhi /ncr", "delhi", df_interview$Candidate_native_location)
df_interview$Candidate_native_location <- gsub("- cochin-", "cochin", df_interview$Candidate_native_location)
```

Let's check Permission obtained

```{r}
unique(df_interview$Permissions_obtained)
```

```{r}
df_interview$Permissions_obtained <- gsub("na", NA, df_interview$Permissions_obtained)


df_interview$Permissions_obtained <- gsub("yet to confirm", "no", df_interview$Permissions_obtained)
df_interview$Permissions_obtained <- gsub("not yet", "no", df_interview$Permissions_obtained)
unique(df_interview$Permissions_obtained)
```


Let's check Unscheduled meetings
```{r}
unique(df_interview$Unscheduled_meetings)
```

```{r}
df_interview$Unscheduled_meetings <- gsub("na", NA, df_interview$Unscheduled_meetings)
df_interview$Unscheduled_meetings <- gsub("not sure", "unsure", df_interview$Unscheduled_meetings)
df_interview$Unscheduled_meetings <- gsub("cant say", "unsure", df_interview$Unscheduled_meetings)
unique(df_interview$Unscheduled_meetings)
```

Let's check follow-up attendance
```{r}
unique(df_interview$follow_up_attendance)
```

```{r}
df_interview$follow_up_attendance <- gsub("na", NA, df_interview$follow_up_attendance)
df_interview$follow_up_attendance <- gsub("no dont", "no", df_interview$follow_up_attendance)
unique(df_interview$follow_up_attendance)
```

Let's check Alt Number
```{r}
unique(df_interview$Alt_number)
```

```{r}
df_interview$Alt_number <- gsub("na", NA, df_interview$Alt_number)
df_interview$Alt_number <- gsub("no i have only thi number", "no", df_interview$Alt_number)
unique(df_interview$Alt_number)
```

Let's check Printout taken
```{r}
unique(df_interview$Printout_taken)
```

```{r}
df_interview$Printout_taken <- gsub("na", NA, df_interview$Printout_taken)
df_interview$Printout_taken <- gsub("not yet", "no", df_interview$Printout_taken)
df_interview$Printout_taken <- gsub("no- will take it soon", "no", df_interview$Printout_taken)
unique(df_interview$Printout_taken)
```

Let;s check clear details
```{r}
unique(df_interview$Clear_details)
```

```{r}
df_interview$Clear_details <- gsub("na", NA, df_interview$Clear_details)
df_interview$Clear_details <- gsub("no- i need to check", "no", df_interview$Clear_details)
unique(df_interview$Clear_details)
```

Let's check call letter
```{r}
unique(df_interview$Call_letter)
```

```{r}
df_interview$Call_letter <- gsub("na", NA, df_interview$Call_letter)
df_interview$Call_letter <- gsub("havent checked", "unsure", df_interview$Call_letter)
df_interview$Call_letter <- gsub("need to check", "unsure", df_interview$Call_letter)
df_interview$Call_letter <- gsub("not sure", "unsure", df_interview$Call_letter)
df_interview$Call_letter <- gsub("yet to check", "unsure", df_interview$Call_letter)
df_interview$Call_letter <- gsub("not yet", "unsure", df_interview$Call_letter)
unique(df_interview$Call_letter)
```

Lets' check expected attendance

```{r}
unique(df_interview$Expected_attendance)
```

```{r}
df_interview$Expected_attendance <- gsub("11:00 am", "yes", df_interview$Expected_attendance)
df_interview$Expected_attendance <- gsub("10.30 am", "yes", df_interview$Expected_attendance)
unique(df_interview$Expected_attendance)
```

```{r}

```

