---
title: "The Interview Attendance Problem"
output: html_notebook
---

Read the data

```{r}
library(readr)
df_interview <- read_csv("Interview.csv")
head(df_interview)
```

```{r}
dim(df_interview)
```

It can be seen that there are NA values in many columns and last 5 columns are empty. So let's get rid of them first.
```{r}
df_interview <- subset(df_interview, select = -c(X24, X25, X26, X27, X28))
head(df_interview)
```

There are long names of columns, that can be quite difficult to handle. Let's change the column names.

```{r}
colnames(df_interview)
```

```{r}
new_col <- c("Date", "Client_name", "Industry", "Location",
             "Position", "SkillSet", "Interview_type", "Candidate_name",
             "Gender", "Current_location", "Job_location", "Venue_of_interview",
             "Candidate_native_location", "Permissions_obtained", "Unscheduled_meetings",
             "follow_up_attendance", "Alt_number", "Printout_taken", "Clear_details",
             "Call_letter", "Expected_attendance", "Observed_attendance", "Marital_status")
colnames(df_interview) <- new_col
colnames(df_interview)
```

# Data Cleaning

Let's check each column for inconsistencies in the data

Let's check Date...
```{r}
unique(df_interview$Date)
```

There are different formats of the date here.

```{r}
library(lubridate)
df_interview$Date <- gsub("&.*", "", df_interview$Date)
df_interview$Date <- dmy(df_interview$Date)
unique(df_interview$Date)
```

Let's check Client_name...
```{r}
unique(df_interview$Client_name)
```

```{r}
df_interview$Client_name <- gsub("Standard Chartered Bank Chennai", "Standard Chartered Bank", df_interview$Client_name)
df_interview$Client_name <- gsub("Aon hewitt Gurgaon", "Hewitt", df_interview$Client_name)
df_interview$Client_name <- gsub("Aon Hewitt",  "Hewitt", df_interview$Client_name)
unique(df_interview$Client_name)
```

Let's check Industry...
```{r}
unique(df_interview$Industry)
```

```{r}
df_interview$Industry <- gsub("IT Products and Services", "IT", df_interview$Industry)
df_interview$Industry <- gsub("IT Services", "IT", df_interview$Industry)
unique(df_interview$Industry)
```

Let's check Location...
```{r}
unique(df_interview$Location)
```

```{r}
df_interview$
```

